### 2017-10-09 TF-vldb2018/sec-tsim.tex

%\vspace{-4ex}
\subsection{Team Formation}
\label{subsec-extsim}

@@

Intuitively, $f_P(u)$ specifies a range bound for node $u$,
indicating the required quantity for the matched nodes in data graphs.
Note that for traditional patterns~\cite{Galla06, b-matching,FanLMTWW10,FanCount16}, bounds are typically carried on edges, not on nodes.

We also also denote data and pattern graphs as $G(V$, $E)$ and $P(V_{P}$, $E_{P})$ respectively. The size of $G$ (resp. $P$), denoted by $|G|$ (resp. $|P|$), is defined to be the total number of nodes and edges in $G$ (resp. $P$).

@@

\stitle{Remarks}.
(1) Team simulation differs from graph simulation~\cite{infsimu95} and strong simulation~\cite{MaCFHW14} in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.

\sstab(2) Different from strong simulation with balls having a fixed radius (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is flexible, and is only less than a user specified upper bound.

@@

Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.
 It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
\ie handling continuous separate and simultaneous pattern and data updates.

>>>>

%\vspace{-4ex}
\subsection{Team Simulation}
\label{subsec-extsim}

@@

Intuitively, $f_P(u)$ specifies a range bound for node $u$,
indicating the required quantity for the matched nodes in data graphs.
Note that for traditional patterns~\cite{Galla06, b-matching,FanLMTWW10,FanCount16}, bounds are typically carried on edges, not on nodes.
We also also denote data and pattern graphs as $G(V$, $E)$ and $P(V_{P}$, $E_{P})$ respectively. The size of $G$ (resp. $P$), denoted by $|G|$ (resp. $|P|$), is defined to be the total number of nodes and edges in $G$ (resp. $P$).

@@

\vspace{-1ex}
\stitle{Remarks}.
(1) Team simulation differs from graph simulation~\cite{infsimu95} and strong simulation~\cite{MaCFHW14} in the existence of capacity bounds on pattern graphs and its ability to capture matches on undirected graphs.

\sstab(2) Different from strong simulation with a fixed radius for balls (\ie the diameter of a pattern), team simulation adopts a more natural setting that the radius of the balls is auto-adjustable, having a user specified upper bound only.

@@

Here $\oplus$ denotes applying changes $\Delta P$ to $P$ and $\Delta G$ to $G$, and
 $P\oplus\Delta P$ and $G\oplus\Delta G$ denote the updated pattern and data graphs.
 It is worth mentioning that \dynteamF{} covers a broad range of dynamic situations,
\ie handling continuously separate and simultaneous pattern and data updates.
